Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-11 Paper.Rmd
after ncsurrog modification

We used our four multivariate data sets : aphid-count data, aphid-first flight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We carried out the analysis mentioned in the concepts above, with aphid abundance and aphid first flight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. For example, Figure \ref{fig_skewness_spearman} represents the results for each data set with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the green-spruce aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the nonparametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was significantly higher than expected if the leaf-plum curling aphid first flight data came from a normal copula, which was also confirmed by upper-tail dependence results from model selection and nonparametric results (see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on nonparametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was found significantly lower in comparison to its Normal surrogates (Figure \ref{fig_skewness_spearman} D). We found the same result with all data sets when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}).

@@

Spatial Taylor's law, the observed linear relationship between `log`(variance) and `log`(mean) of population densities of a species from different locations, is a well-known pattern found in ecology and related fields [@Taylor1961, @Taylor1988, @Cohen2013, @Doring2015, @Kuo2016, @Xu2016, @Reuman2017]. We already showed through simulation (Appendix \ref{SM-Consequence_TL_simulation}) that for asymmetric copula this linear relationship somehow deviates compared to Normal copula for a distribution with gamma marginals. We tested spatial Taylor's law with aphid count data (for all 20 species) and found that the mean curvature of the regression line from `log`(variance) vs. `log`(mean) of population abundance data was significantly different from $10000$ Normal surrogates (Spearman-correlation and marginal distribution preserving) for $25\%$ of total species considered. For example, the "Corn leaf aphid" (having significantly upper tail dependence from model selection and nonparametric analysis) showed mean curvature of regression line close to zero, whereas `r 10000 -(tlsp6$p_left_mncurv*10000)` of the $10000$ Normal surrogates showed higher curvature, indicating here Normal copula didn't hold linear relationship between `log`(spatial variance) and `log`(spatial mean) (see Fig \ref{fig_sTL_mncurv_sp6}).

>>>>

We used our four multivariate data sets : aphid-count data, aphid-first flight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We carried out the analysis mentioned in the concepts above for spearman preserving surrogates, with aphid abundance and aphid first flight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. For example, Figure \ref{fig_skewness_spearman} represents the results for each data set with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the green-spruce aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the nonparametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was significantly higher than expected if the leaf-plum curling aphid first flight data came from a normal copula, which was also confirmed by upper-tail dependence results from model selection and nonparametric results (see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on nonparametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was found significantly lower in comparison to its Normal surrogates (Figure \ref{fig_skewness_spearman} D). 
<!--We found the same result with all data sets when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}). Now we did only with spearman preserving to handle ties and +ve semidefinite case-->

@@

Spatial Taylor's law, the observed linear relationship between `log`(variance) and `log`(mean) of population densities of a species from different locations, is a well-known pattern found in ecology and related fields [@Taylor1961, @Taylor1988, @Cohen2013, @Doring2015, @Kuo2016, @Xu2016, @Reuman2017]. We already showed through simulation (Appendix \ref{SM-Consequence_TL_simulation}) that for asymmetric copula this linear relationship somehow deviates compared to Normal copula for a distribution with gamma marginals. We tested spatial Taylor's law with aphid count data (for all 20 species) and found that the mean curvature of the regression line from `log`(variance) vs. `log`(mean) of population abundance data was significantly different from $10000$ Normal surrogates (Spearman-correlation and marginal distribution preserving) for $20\%$ of total species considered. For example, the "Corn leaf aphid" (having significantly upper tail dependence from model selection and nonparametric analysis) showed mean curvature of regression line close to zero, whereas `r 10000 -(tlsp6$p_left_mncurv*10000)` of the $10000$ Normal surrogates showed higher curvature, indicating here Normal copula didn't hold linear relationship between `log`(spatial variance) and `log`(spatial mean) (see Fig \ref{fig_sTL_mncurv_sp6}).

### 2019-02-11 SupportingInformation.Rmd
after ncsurrog modification

# For sp =1, sp=4 and sp=6 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite : you can see those msg by deleting results="hide" and warning=F option in r chunk

@@

skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid count","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_count_kendall$realskw[i]<-ans$realskw
  skw_aphid_count_kendall$p_left[i]<-p_left
  skw_aphid_count_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

@@

# For sp =12 and sp=16 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite : you can see those msg by deleting results="hide" and warning=F option in r chunk

@@

skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=25,width=25)
op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
cat("Now for kendall preserving surrogs : aphid ff","\n")
for(i in splist){
  cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
  skw_aphid_ff_kendall$p_left[i]<-p_left
  skw_aphid_ff_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

@@

# There is no error msg or warning coming from ncsurrog : ncov semidefinite matrix for any species with spearman
# or kendall preserving surrogates.

@@

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="kendall") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_kendall$realskw[i]<-ans$realskw
  skw_plankton_kendall$p_left[i]<-p_left
  skw_plankton_kendall$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

@@

@@

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
par(op)
dev.off()

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall") 
p_left<-sum(answer3k$surrogskw < answer3k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="kendall") 
p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()

@@

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf}
\includegraphics[width=8 cm]{./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf}
\caption{Skewness of spatially averaged $(A)$ Green-spruce aphid's abundance, $(B)$ Leaf-plum curling aphid's firstflight date, $(C)$ Ceratium furca's abundance and $(D)$ methane-flux data, were indicated by red dot in each plot and were compared with respect to skewness of spatially averaged 10000 Normal surrogates preserving Kendall correlation). \label{fig_skewness_kendall}}
\end{center}
\end{figure}

>>>>

# For sp =1, sp=4 and sp=6 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite
# also it can't handle ties for "kendall" and code crashes
# you can see those msg by deleting results="hide" and warning=F option in r chunk

@@

#skw_aphid_count_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
#colnames(skw_aphid_count_kendall)<-c("realskw","p_left","p_right")
#rownames(skw_aphid_count_kendall)<-paste("sp",splist,sep="")
#pdf("./Results/skewness_results/skewness_aphid_count/aphid_count_allsp_skewness_kendall.pdf",height=25,width=25)
#op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : aphid count","\n")
#for(i in splist){
#  cat("sp=",i,"\n")
#  loclist<-good_loclist(d_allsp=data_aphid_count,sp=i,data_pt_thrs=30)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_count),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
# p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_aphid_count_kendall$realskw[i]<-ans$realskw
#  skw_aphid_count_kendall$p_left[i]<-p_left
#  skw_aphid_count_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_aphid_count_kendall,"./Results/skewness_results/skewness_aphid_count/skw_aphid_count_kendall.RDS")
```

@@

# For sp =12 and sp=16 : kendall preserving surrogates gives warning : Error in ncsurrog: ncov is not positive semidefinite,
# also it can't handle ties for "kendall" and code crashes
# you can see those msg by deleting results="hide" and warning=F option in r chunk

@@

#skw_aphid_ff_kendall<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
#colnames(skw_aphid_ff_kendall)<-c("realskw","p_left","p_right")
#rownames(skw_aphid_ff_kendall)<-paste("sp",splist,sep="")
#pdf("./Results/skewness_results/skewness_aphid_ff/aphid_ff_allsp_skewness_kendall.pdf",height=25,width=25)
#op<-par(mfrow=c(4,5),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : aphid ff","\n")
#for(i in splist){
#  cat("sp=",i,"\n")
#  loclist<-good_loclist(d_allsp=data_aphid_ff,sp=i,data_pt_thrs=30)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_aphid_ff),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
#  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_aphid_ff_kendall$realskw[i]<-ans$realskw
#  skw_aphid_ff_kendall$p_left[i]<-p_left
#  skw_aphid_ff_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_aphid_ff_kendall,"./Results/skewness_results/skewness_aphid_ff/skw_aphid_ff_kendall.RDS")
```

@@

# There is no error msg or warning coming from ncsurrog : ncov semidefinite matrix for any species with spearman or kendall preserving surrogates.
# But there may be error handling ties with "kendall"
# So,for safety, now we will only analyze with "spearman"

@@

splist<-c(1:22)
skw_plankton_spearman<-as.data.frame(matrix(NA,nrow=length(splist),ncol=3))
colnames(skw_plankton_spearman)<-c("realskw","p_left","p_right")
rownames(skw_plankton_spearman)<-paste("sp",splist,sep="")
#skw_plankton_kendall<-skw_plankton_spearman
pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_spearman.pdf",height=30,width=30)
op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for spearman preserving surrogs : pns","\n")
for(i in splist){
  #cat("sp=",i,"\n")
  loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
                        numsurrog=numsurrog,
                        ploton=T,
                        corpres="spearman") 
  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
  skw_plankton_spearman$realskw[i]<-ans$realskw
  skw_plankton_spearman$p_left[i]<-p_left
  skw_plankton_spearman$p_right[i]<-p_right
  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
}
par(op)
dev.off()
saveRDS(skw_plankton_spearman,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_spearman.RDS")

#pdf("./Results/skewness_results/skewness_plankton_north_sea/plankton_allsp_skewness_kendall.pdf",height=30,width=30)
#op<-par(mfrow=c(4,6),mar=c(5,5,1,1),mgp=c(3,1,0))
#cat("Now for kendall preserving surrogs : pns","\n")
#for(i in splist){
  #cat("sp=",i,"\n")
 # loclist<-good_loclist(d_allsp=data_plankton_north_sea,sp=i,data_pt_thrs=45)
#  ans<-skewness_testing(ts_matrix=sp_data(sp=i,d_allsp=data_plankton_north_sea),loclist=loclist,
#                        numsurrog=numsurrog,
#                        ploton=T,
#                        corpres="kendall") 
#  p_left<-sum(ans$surrogskw < ans$realskw)/numsurrog
#  p_right<-sum(ans$surrogskw > ans$realskw)/numsurrog
#  skw_plankton_kendall$realskw[i]<-ans$realskw
#  skw_plankton_kendall$p_left[i]<-p_left
#  skw_plankton_kendall$p_right[i]<-p_right
#  mtext(paste0("sp = ",i,", p_left = ",p_left,", p_right = ",p_right),side=3,line=-0.5,col="navyblue",cex = 1)
#}
#par(op)
#dev.off()
#saveRDS(skw_plankton_kendall,"./Results/skewness_results/skewness_plankton_north_sea/skw_plankton_kendall.RDS")
```

@@

# Only done for "Spearman" method

@@

#pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_kendall.pdf",height=6,width=8)
#op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
#answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
#                          corpres="kendall") 
#p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
#mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
#par(op)
#dev.off()

@@

#pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_kendall.pdf",height=6,width=8)
#op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
#answer2k<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
#                          corpres="kendall") 
#p_right<-sum(answer2k$surrogskw > answer2k$realskw)/numsurrog
#mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
#par(op)
#dev.off()

@@

#pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_kendall.pdf",height=6,width=8)
#op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
#answer3k<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
#                          corpres="kendall") 
#p_left<-sum(answer3k$surrogskw < answer3k$realskw)/numsurrog
#mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
#par(op)
#dev.off()

@@

#pdf("./Results/skewness_results/skewness_methane/skewness_methane_kendall.pdf",height=6,width=8)
#op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
#answer1k<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
#                           corpres="kendall") 
#p_left<-sum(answer1k$surrogskw < answer1k$realskw)/numsurrog
#mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
#par(op)
#dev.off()

@@
